\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Presentation Assignment: Controversies and Solutions in Software and Music Piracy}
\MYHEADERS{Presentation Assignment}{Controversies and Solutions}

\vspace*{-.2in}
\begin{center}
	{\bf Due Date: Monday or Wednesday, October 28 or 30, 2013}
\end{center}

Prepare and give a short four to six minute presentation about an interesting and/or controversial topic related to the
theme software and music piracy. In particular, your presentation should focus on the content that we have studied in
the third module of the course. Your presentation should start with a short one sentence title and later include a clear
statement of your viewpoint on the chosen issue. During your presentation, please make sure that you explain the key
issues and then take a stand about the best method(s) for addressing these matters. Whenever possible, the short
presentation should develop concrete examples that clearly support your statements.

Presentations should be logically organized and presented in a professional manner. Students may use a small number of
note cards and/or handouts to support their prepared remarks. Furthermore, you may elect to use several PowerPoint
slides for this short presentation. Furthermore, all students must strictly adhere to the time limit. That is, students
must ensure that their talk is not shorter than four minutes and not longer than six minutes. Timing software will be
used during your presentations to make sure that you adhere to the stated time limit. Students are strongly encouraged
to discuss their presentation ideas with the instructor. Students should consider conducting practice presentations in
front of their peers so that they can develop a feel for what it is like to stand in front of an audience.

\end{document}
