\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Short Writing Assignment: Titles and Thesis Statements}
\MYHEADERS{Short Writing Assignment}{Titles and Thesis Statements}

\vspace*{-.2in}
\begin{center}
	{\bf Due Date: Friday, October 11, 2013}
\end{center}

In the class session today, you will work in a team to individually develop a thesis statement and a title for an essay.
In collaboration with your team members, please revise and improve these items to make sure that they carefully connect to
the reading assignments and the theme of this module.  After you are convinced that the thesis statement meets the
criteria in {\em A Writer's Reference} and the title adheres to the guidelines that we previously outlined in class, please
write a short two page essay that explores your thesis in greater detail. As you are writing, you should focus on citing
and developing concrete examples that illustrate your point.

Once today's class session is finished, you are responsible for writing an essay that further explores the thesis
statement that you developed. As you are writing your essay, each of your team members will serve as your editor,
reading drafts of your content and providing you with substantive comments about your paper. Before turning in this
assignment, you must meet with your team at least once outside of our class sessions. Please record the date and the
elapsed time of the meeting(s) with your editors. Furthermore, you are responsible for keeping and turning in all of the
marked versions of your paper that were created by your editors.

Before you leave the class session today, you should exchange contact information with your team members and agree on a
time when you will meet again to review drafts of your papers.

Finally, all students are encouraged to bring a draft of their materials to the Learning Commons and/or the instructor's office
hours in order to receive extra feedback on their writing assignment.

\end{document}
