\documentclass[12pt]{article}
\textwidth = 6.5in
\textheight = 9.05in
\topmargin 0.0in
\oddsidemargin 0.0in
\evensidemargin 0.0in

\usepackage[T1]{fontenc}

% set it so that subsubsections have numbers and they
% are displayed in the TOC (maybe hard to read, might want to disable)

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\usepackage{epsfig}

% define widow protection 
        
\def\widow#1{\vskip #1\vbadness10000\penalty-200\vskip-#1}

% define a little section heading that doesn't go with any number

\def\littlesection#1{
\widow{2cm}
\vskip 0.5cm
\noindent{\bf #1}
\vskip 0.1cm
\noindent
}

% A paraphrase mode that makes it easy to see the stuff that shouldn't
% stay in for the final proposal

\newdimen\tmpdim
\long\def\paraphrase#1{{\parskip=0pt\hfil\break
\tmpdim=\hsize\advance\tmpdim by -15pt\noindent%
\hbox to \hsize
{\vrule\hskip 3pt\vrule\hfil\hbox to \tmpdim{\vbox{\hsize=\tmpdim
\def\par{\leavevmode\endgraf}
\obeyspaces \obeylines 
\let\par=\endgraf
\bf #1}}}}}

\renewcommand{\baselinestretch}{1.2}    % must go before the begin of doc

% go with the way that CC sets the margins

\pagestyle{empty}

\begin{document}

% handle widows appropriately
\def\widow#1{\vskip #1\vbadness10000\penalty-200\vskip-#1}

\begin{center}

FS 101: Software Everywhere \\
Final Examination \\
%Friday, November 2, 2007 \\

\end{center}

\noindent
Answer the eight questions that are listed on the following sheets.  You
must provide answers to these questions on a separate sheet of paper.
Please develop responses that clearly express your ideas in the most
succinct manner possible.  You are not permitted to complete this
examination in conjunction with any of your classmates.  Furthermore,
you cannot consult any outside references during this examination.  If
you have questions concerning the problems, then please visit my
office during the examination period.  If you leave the classroom to
take the exam, then you are responsible for checking the chalk board
for status updates.

\newpage

\begin{enumerate}

\item ({\bf 10 Points}) Answer the following questions about Richard
  Hamming and his ``You and Your Research'' presentation.


\begin{enumerate}

\item ({\bf 4 Points}) In his ``You and Your Research'' presentation
  Hamming asks and answers the question ``why do so few scientists
  make significant contributions and so many are forgotten in the long
  run?''  What are some of the responses that Hamming gives to this
  question?

\item ({\bf 4 Points}) Hamming makes the observation that ``knowledge
  and productivity are like compound interest.''  What does this mean?

\item ({\bf 2 Points}) The ``You and Your Research'' speech contains a
  number of controversial statements.  Pick one of these observations
  and then state whether you agree or disagree with it.  Your response
  to this question should also fully explain why you agree or
  disagree with Hamming's observation.

\end{enumerate}

\newpage

\item ({\bf 10 Points}) Answer the following questions about the
  famous --- and rather quirky! --- mathematician named Paul
  Erd\"{o}s.

\begin{enumerate}

\item ({\bf 4 Points}) Paul Erd\"{o}s was known as the ``man who loved
  only numbers.''  Beyond being a mathematician who was in love with
  numbers, who was Paul Erd\"{o}s?  Your response to this question
  should also give one important contribution of Erd\"{o}s.

\item ({\bf 4 Points}) Paul Erd\"{o}s was addicted to amphetamines.
  In your judgment, was it appropriate for this mathematician to take
  these drugs in order to enhance his contribution to his discipline?

\item ({\bf 2 Points}) Intuitively explain the concept of the
  Erd\"{o}s number.  Do mathematicians and scientists seek to have a
  low or a high Erd\"{o}s number?  Why?

\end{enumerate}

\newpage

\item ({\bf 10 Points}) Answer the following questions about Google, a well-known company. 

\begin{enumerate}

  \item ({\bf 2 Points}) A recent article in the {\em New York Times} introduces the concept of a {\em Xoogler}.  What
    is the meaning of this term?

  \item ({\bf 2 Points}) Google is developing a new type of car.  What kind of car is it? What are some of the
    implications associated with the use of this type of car?
  
  \item ({\bf 6 Points}) Google has developed a wide variety of software and hardware products.  Without referencing the
    Google car, please name six of these products and explain how they fit into Google's overarching business goals.


\end{enumerate}

\newpage

\item ({\bf 10 Points}) Answer the following questions about the
  purposes of education in high school and college, as expressed by
  Dominic Randolph and Louis Menand.

\begin{enumerate}

\item ({\bf 5 Points}) In a New York Times article entitled ``What if
  the Secret to Success if Failure?'' Dominic Randolph is quoted as
  saying that ``This push on tests is missing out on some serious
  parts of what it means to be a successful human.''  What is the
  critical piece of education that Randolph thinks is missing? Do you
  agree or disagree with Randolph's viewpoint?

\item ({\bf 5 Points}) Louis Menand develops several theories about why
  colleges and universities exist in the United States of America.
  What are these reasons?  After clearly explaining each of the
  theories, you should discuss which one you think is the most
  appropriate viewpoint.

\end{enumerate}

\newpage

%% \item ({\bf 10 Points}) Answer the following questions about Carl
%%   Sagan and his speech about a ``pale blue dot.''

%% \begin{enumerate}

%% \item ({\bf 4 Points}) Carl Sagan gave a speech where he referenced
%%   ``a pale blue dot.''  In reality, what is this dot?

%% \item ({\bf 6 Points}) Carl Sagan makes the observation that ``the
%%   Earth is a very small stage in a vast cosmic arena.''  What does
%%   this statement mean?  How does Sagan use the ``pale blue dot'' to
%%   justify this assertion?

%% \end{enumerate}

\item ({\bf 10 Points}) Answer the following questions about software
  and music piracy.

\begin{enumerate}

\item ({\bf 5 Points}) Malin and Flowers find that, for 200 suburban
  high school students from the New York metropolitan area, there is
  one dominant predictor for whether or not an individual will pirate.
  What is this predictor?  Why is it so effective at predicting
  whether or not a high school student will pirate music?

%% \item ({\bf 3 Points}) The Malin and Flowers study also looked at
%%   whether age and grade level could have an impact on music piracy.
%%   Do their findings suggest that 9th or 12th graders are more likely
%%   to pirate music?  Why do you think that they found this result?

\item ({\bf 5 Points}) Name at least two different programs that you
  can use to pirate music or software.  How do these programs work?
  What are their strengths and weaknesses?  If possible, your response
  to this question should use a diagram to explain the way that your
  chosen programs work.

\end{enumerate}

\newpage

%% \item ({\bf 10 Points}) Answer the following questions about how
%%   various companies and individuals, such as Google and Derek Webb,
%%   are taking steps to change the \mbox{future of music}.

%% \begin{enumerate}

%% \item ({\bf 5 Points}) Google Greater China's president recently
%%   describe the company's new initiative as a ``huge leap of faith for
%%   us.''  What type of new service is Google now offering in China?  Do
%%   you agree or disagree with this approach taken by Google?  Why do
%%   you think that Google is taking these steps?

%% \item ({\bf 5 Points}) In his ``Feedback'' blog, Derek Webb writes
%%   that ``There has never been a better moment to be a middle-class or
%%   an independently thinking artist making and performing music than
%%   right now.''  Why does Webb make this statement?  How does Webb
%%   suggest that music artists make a living?

%% \end{enumerate}

\newpage

%% \item ({\bf 10 Points}) Answer the following questions about the use
%%   of computer software during the education of elementary school
%%   students.

%% \begin{enumerate}

%% \item ({\bf 6 Points}) The authors of the article
%%   ``Scratch:\ Programming for All'' furnish their own definition of
%%   the term {\em digital fluency} --- what is it?  The authors of this
%%   article also argue that certain types of interactions with software
%%   and technology are {\em not} examples of digital fluency --- what
%%   are they?

%% \item ({\bf 4 Points}) In their article ``Empowering Kids to Create
%%   and Share Programmable Media'' the authors outline the following
%%   types of individuals who may use software and technology: passive
%%   consumer, active consumer, passive producer, and active producer.
%%   What is the meaning of each of these terms?

%% \end{enumerate}

\newpage

\item ({\bf 10 Points}) Answer the following questions about the
  practice of plagiarism and the rise of computer software and
  technology.

\begin{enumerate}

\item ({\bf 6 Points}) My paper ``Time-Aware Test Suite
  Prioritization'' was recently plagiarized by researchers in India.
  Please classify this activity of plagiarism according to the
  following scale for the ``seven deadly sins of plagiarism.''  Your
  response to this question should furnish concrete evidence to
  support your classification.

  \begin{enumerate}

  \item Intentional grand larceny
  \item Premeditated shoplifting
  \item Tinkering with the evidence
  \item Idea kidnapping
  \item Unauthorized borrowing of private property
  \item Trespassing over boundaries
  \item Writing under the influence

  \end{enumerate}

\item ({\bf 2 Points}) Trip Gabriel contends that living in the
  ``digital age'' has caused plagiarism lines to blur for college
  students.  Why does Gabriel make this assertion?  Do you agree with
  his statement?

\item ({\bf 2 Points}) Briefly summarize the Allegheny College honor
  code.

\end{enumerate}

\newpage

%% \item ({\bf 10 Points}) Answer the following questions about the
%%   recent activities of the Google Corporation.

%% \begin{enumerate}

%% \item ({\bf 6 Points}) Edward Wyatt reports in his New York Times
%%   article that Google and Verizon are working to establish ``tiers''
%%   on the Internet.  What are these tiers?  Why do Google and Verizon
%%   want to create them?  Do you agree or disagree with this approach?
%%   Why?

%% \item ({\bf 2 Points}) John Markoff of the New York Times reports that
%%   Google is developing their own car.  What are the most important
%%   features of this vehicle?

%% \item ({\bf 2 Points}) Name two products that people currently
%%   associate with Google.  Your response to this question should
%%   briefly explain how this product works and the way it fits into
%%   Google's business plan.

%% \end{enumerate}

\newpage

\item ({\bf 10 Points}) Answer the following questions about the
  ``BUGS in Writing'' book.

\begin{enumerate}

\item ({\bf 6 Points}) Lyn Dupre introduces the BUGS scale in order to
  evaluate the quality of a person's writing.  What is the BUGS scale?  In
  your judgment, how did you rank on the BUGS scale at the start of
  the semester?  How do you think that you would rank on the scale at
  the end of the semester? Why?

\item ({\bf 2 Points}) Dupre's preface to the ``BUGS in Writing'' book
  develops the concept of {\em ear} --- what does this term mean?

\item ({\bf 2 Points}) A book about the principles of writing can
  either be {\em descriptive} or {\em prescriptive} in nature.  Is
  ``BUGS in Writing'' descriptive or prescriptive?

\end{enumerate}

\newpage

\item ({\bf 10 Points}) Answer the following questions about the use
  of proper grammar in English language sentences.  For the first four
  of these questions, you should state whether the sentence is written
  properly.  If it is correct, then you should explain what rule(s)
  the sentence properly follows.  If there is a mistake in the
  sentence, then you should identify it and provide a correction.

\begin{enumerate}

%% \item ({\bf 2 Points}) Is this sentence correct?

  %% \begin{quote}

  %%   The IBM computer that has the most bells and whistels will sell
  %%   the fastest.

  %% \end{quote}

\item ({\bf 2 Points}) Is this sentence correct?

  \begin{quote}

    When memory is so short that it cannot be freed sufficiently fast
    to satisfy demand, swapping can be used.

  \end{quote}

\item ({\bf 2 Points}) Is this sentence correct?

  \begin{quote}

    Donald Knuth looked for an algorithm to solve the problem with.

  \end{quote}

\item ({\bf 2 Points}) Is this sentence correct?

  \begin{quote}

    People that never express emotions are boring; they are entirely
    too predictable.

  \end{quote}

\item ({\bf 2 Points}) In the handbook ``A Writer's Reference'' Hacker
  and Sommers describe the idea of a {\em thesis statement} --- what
  is it and why do the authors argue that writers should include one
  in their papers?

\item ({\bf 2 Points}) In the ``{They Say/I Say}'' book, the authors
  introduce the idea of writing {\em templates}.  What is the purpose
  of these templates?  Do you think that it is a good idea to use
  them?

\end{enumerate}

\end{enumerate}

\end{document}



