\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Long Writing Assignment: A Personal Perspective of ``Software Everywhere''}
\MYHEADERS{Long Writing Assignment}{Personal Perspective}

\vspace*{-.2in}
\begin{center}
	{\bf Due Date: Wednesday, October 30, 2013}
\end{center}

This assignment invites you to complete a ten page ``portrait in piracy''.  You are responsible for interviewing
individuals who can share an interesting, informative, and balanced account about software and/or music piracy. 
For this assignment, you may want to interview individuals who are strongly in support of or opposed to software and music
piracy. Students are encouraged to pick interview candidates who may hold an opinion that is very different from their
own. Before conducting your interview, please carefully think about the people who will answer your questions and
then prepare a detailed listing of the issues that you want to examine during your time together. Once the interviews are
finished and you have recorded all of the responses, you should prepare a written report on the interviews.  Going beyond a
simple restatement of the questions and the answers, this paper should include personal insights, additional facts and
details, counterpoints to stated opinions, and other content that would yield a nuanced portrait in piracy.

As in the previous writing assignments, you should create an interesting title that directly connects to the main point
of your interviews. You must organize your document into sections and paragraphs that each develop a single concept. If
the interviewees refer to ideas or concepts that may not be familiar to your readers, then you should use and cite the
sources that properly explain these issues. When you are writing your article, you must correct all spelling, grammar,
and formatting errors. You are also required to type the assignment using a modern word processor (i.e., hand-written
assignments are not acceptable). Students should strongly consider using desktop publishing software to format their
article in a professional fashion. Your final submission must include all brainstorming notes, the
final version of your interview questions, the notes that you took during the interview, and the final version of the
document containing your structured interview.

Just like in the past writing assignment, you should work with a team as you complete this assignment.  As you
participate in the team, you are responsible for acting as an editor for every other member of the team.  Moreover, you
must ask your team members to edit your paper on two separate occasions.  That is, during two distinct meetings each
member of your team should read and comment on a rough draft and a final draft of your paper; you should do the same for
each of the other members of your team. Before you leave the class session today, you should exchange contact
information with your team members and agree on times when you will meet again to review drafts of your paper.  In
advance of leaving the classroom, please submit to the instructor a printed document listing the names of your team
members and your meeting times. Along with the previously mentioned deliverables, you also must
submit all of the marked versions of your paper.

Finally, all students are encouraged to bring a draft of their materials to the
Learning Commons and/or the instructor's office hours in order to receive extra feedback on their writing assignment.

\end{document}
