\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Presentation Assignment: Controversies and Solutions in Software and Plagiarism}
\MYHEADERS{Presentation Assignment}{Controversies and Solutions}

\vspace*{-.2in}
\begin{center}
	{\bf Due Date: Friday or Monday, November 22 or 25, 2013}
\end{center}

Prepare and give a short four to six minute presentation about an interesting and controversial topic related to the
theme of software and plagiarism. In particular, your presentation should focus on the content that we have studied in
the fourth module of the course. Your presentation should start with a short one sentence title and later include a clear
statement of your viewpoint on the chosen issue. During your presentation, please make sure that you explain the key
issues and then take a stand about the best method(s) for addressing these matters. Whenever possible, the short
presentation should develop concrete examples that clearly support your statements.

Presentations should be logically organized and presented in a professional manner. To support your presentation, you
should program simple slides using the HTML-based approach that we have practiced in class. Furthermore, all
students must strictly adhere to the time limit. That is, students must ensure that their talk is not shorter than four
minutes and not longer than six minutes. Timing software will be used during your presentations to make sure that you
adhere to the stated time limit. Students are strongly encouraged to discuss their presentation ideas with the
instructor.  You should also consider conducting practice presentations in front of your peers so that you can develop
a better feel for what it is like to stand in front of an audience.

During the presentations, all students will be required to evaluate both themselves and all other students.  The student(s)
who receive the highest overall numerical evaluation from their peers and the instructor will have their letter grade
for the presentation increased by a half letter grade.

`` this is a test ''

\end{document}
