\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Long Writing Assignment: Portrait in Piracy}
\MYHEADERS{Long Writing Assignment}{Portrait in Piracy}

\vspace*{-.2in}
\begin{center}
	{\bf Due Date: Wednesday, October 30, 2013}
\end{center}

In this assignment, you must complete a six to eight page portrait in piracy.  You are responsible for interviewing
individual(s) who can share an interesting and informative account about either software or music piracy. For instance,
you may decide to interview someone who was previously sued by the Recording Industry Association of America (RIAA).
Alternatively, you may want to interview individual(s) who are strongly in support of or opposed to software and music
piracy. Students are encouraged to pick interview candidate(s) who may hold an opinion that is very different from their
own. Before conducting your interview, please think carefully about the person(s) who will answer your questions and
then prepared a detailed listing of issues that you want to examine during your time together. Once the interview is
finished and you have recorded all of their responses, you should prepare a written record of the interview following
the style of Donald Knuth's interviews in Communications of the ACM.

As in the previous writing assignments, you should create an interesting title that directly connects to the main point
of your interview. You must organize your document into sections and paragraphs that each develop a single concept. If
the interviewee(s) refer to ideas or concepts that may not be familiar to your readers, then you should use and cite the
sources that properly explain these issues. When you are writing your article, you must correct all spelling, grammar,
and formatting errors. You are also required to type the assignment using a modern word processor (i.e., hand-written
assignments are not acceptable). Your final submission for this assignment must include all brainstorming notes, the
final version of your interview questions, the notes that you took during the interview, and the final version of the
document containing your structured interview.

Before you leave the class session today, you should exchange contact information with your team members and agree on a
time when you will meet again to review drafts of your papers.

Finally, all students are encouraged to bring a draft of their materials to the Learning Commons and/or the instructor's office
hours in order to receive extra feedback on their writing assignment.

\end{document}
