\input{hwpre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Short Writing Assignment: Revising a Writing Assignment}
\MYHEADERS{Short Writing Assignment}{Revising a Writing Assignment}

\vspace*{-.2in}
\begin{center}
	{\bf Due Date: Monday, November 25, 2013}
\end{center}	

This assignment asks you to revise and enhance one of your first four short writing assignments. As you are modifying
one of your first assignments, you must take into account the comments that you received from the instructor and any
feedback that you may have derived from your previously assigned writing teams. When you are working on this
assignment, please review the following readings from Diana Hacker's ``A Writer's Reference'': Pages 10-11 (Section
C1-c), 14-18 (Section C2-a), 81 (Section A2-d), and 373 - 376 (Section MLA-1). Moreover, please read the following new
Hacker reading assignments on pages 20-31 (Section C3), 32-44 (Section C4), and 45 - 62 (Section C5). Finally, you
should review the content from Lyn Dupre's ``BUGS in Writing'': chapters 1, 15, and 23, and any additional
chapter assigned for you to read during the semester.

You must use a modern word processor to prepare your paper and ensure that your document does not have any mistakes in
spelling, grammar, or format. Furthermore, students are strongly encouraged to meet with a writing consultant from the
Learning Commons in order to review the materials that they produce in response to this assignment. All students must
state whether or not they met with a writing consultant near the pledge line on their paper. As always, students
should consider meeting with the instructor of the course to discuss both enhancement ideas for and drafts of their paper. Finally,
students are required to turn in the original --- marked and graded --- version of the paper that they revised as part
of this assignment.

\end{document}
