\input{syllabuspre.tex}

\usepackage[compact]{titlesec}

\begin{document}
\MYTITLE{Syllabus}
\MYHEADERS{Syllabus}{}

\subsection*{Course Instructor}
Dr.\ Gregory M.\ Kapfhammer\\
\noindent Office Location: Alden Hall 108 \\
\noindent Office Phone: +1 814-332-2880 \\
\noindent Email: \url{gkapfham@allegheny.edu} \\
\noindent Twitter: \url{@GregKapfhammer} \\
\noindent Web Site: \url{http://www.cs.allegheny.edu/sites/gkapfham/} 

\subsection*{Instructor's Office Hours}

\begin{itemize}
	\itemsep 0em
	\item Monday: 1:00 pm -- 2:30 pm (30 minute time slots)
	\item Tuesday: 2:30 pm -- 4:00 pm (15 minute time slots)
	\item Wednesday: 4:30 pm -- 5:00 pm (15 minute time slots)
	\item Thursday: 9:00 am -- 10:00 am (15 minute time slots) {\em and} \\ \hspace*{.69in} 2:30 pm -- 4:00 pm (15 minute time slots)
	\item Friday: 1:00 pm -- 2:30 pm (10 minute time slots) {\em and} \\ \hspace*{.49in} 4:30 pm -- 5:00 pm (5 minute time slots)
\end{itemize}

\noindent
To schedule a meeting with me during my office hours, please visit my Web site and click the ``Schedule'' link in the
top right-hand corner. Now, you can browse my office hours or schedule an appointment by clicking the correct link and
then reserving an open time slot. 

\subsection*{Course Meeting Schedule}

Discussion, Presentations, and Group Work: Monday, Wednesday, Friday, 11:00 am -- 11:50 am \\
Final Examination: Tuesday, December 17 at 9:00 am

\subsection*{Course Catalogue Description}

\begin{quote}

An examination of the pervasive nature of computer software and the impact that computer technology has on society.
Drawing on articles from the popular press and the computer science literature, this course examines the technical and
ethical challenges that face a culture that regularly uses computer software applications. Sample topics include the
Internet, Google, online music, open source software, electronic commerce, social networking, and data mining.
Coursework emphasizes the development of effective oral and written communication skills with a focus on description,
summary, and critical thinking.

\end{quote}

\subsection*{Course Objectives}

Beyond the purpose of integrating new students into the intellectual life of Allegheny College, the goal of this course
is to ensure that students are able to effectively write and speak.  Using the theme of ``Software Everywhere'' as an
ends towards achieving these goals, students will learn to write and speak in a variety of styles and on a multitude of
subjects.  Students will also find out about the resources available to and rules and regulations upheld by students at 
Allegheny College.  Finally, students will learn how to competently interact with both their adviser and other
professors.

\subsection*{Performance Objectives}

At the end of this course, students will know how to manage their time in a fashion that will ensure their academic
success at Allegheny College.  Members of the class should be able to confidently write and revise high-quality papers
of less than ten pages and practice and give interesting, exciting, and accurate presentations of no more than five
minutes.  Students should know how to both participate in and lead class discussions, respectfully debate their peers,
actively participate in group work, and interact with the course instructor during both class and advising sessions. 

\subsection*{Required Textbooks}

  % A Writer's Reference [Plastic Comb]
  % Diana Hacker (Author), Nancy Sommers (Author)
  % ISBN-10: 0312601433
  % ISBN-13: 978-0312601430
  % Seventh Edition
  % Status: Required
  % 18 copies

  \noindent{\em A Writer's Reference}. Nancy Sommers. Seventh Edition,  ISBN-10: 0312601433, ISBN-13: 978-0312601430,
  245 pages, 2010.

  % They Say, I Say: The Moves That Matter in Academic Writing [Paperback]
  % Gerald Graff (Author), Cathy Birkenstein (Author)
  % ISBN-10: 039393361X
  % ISBN-13: 978-0393933611
  % Second Edition
  % Status: Required
  % 18 copies

  \noindent{\em They Say, I Say: The Moves That Matter in Academic Writing}. Gerald Graff and Cathy Birkenstein. Second Edition,  
  ISBN-10: 039393361X, ISBN-13: 978-0393933611, 245 pages, 2009.

  % BUGS in Writing, Revised Edition: A Guide to Debugging Your Prose
  % [Paperback]
  % Lyn Dupre (Author)
  % ISBN-10: 020137921X
  % ISBN-13: 978-0201379211
  % Second Edition
  % Status: Required
  % 18 copies

\noindent{\em BUGS in Writing: A Guide to Debugging Your Prose}. Lyn Dupr\'e. Second Edition,  ISBN-10: 020137921X,
ISBN-13: 978-0201379211, 704 pages, 1998.

\noindent
Students wanting to hone their technical writing skills are encouraged to consult the following book.

\noindent{\em Writing for Computer Science}.  Justin Zobel. Second Edition,  ISBN-10: 1852338024, ISBN-13:
978-1852338022, 270 pages, 2004.

\noindent 
Along with reading the required books, you will be asked to study many additional articles from a wide variety of
conference proceedings, journals, and the popular press.

% One important policy to remember: scheduling their advising meeting with me! Make this a part of their grade!

\subsection*{Class Policies}

\subsubsection*{Grading Policy}

The grade that a student receives in this class will be based on the
following categories. All percentages are approximate and it is possible
for the assigned percentages to change during the academic semester if a
need to do so presents itself. 

% <tr>
% <td> Class Participation </td><td>5%</td>
% </tr>
% 
% <tr>
% <td> Instructor and Peer Leader Meetings </td><td>5%</td>
% </tr>
% 
% <tr>
% <td>Short Writing and Presentation Assignments</td><td>60%</td>
% </tr>
% 
% <tr>
% <td>Long Writing Assignments</td><td>10%</td>
% </tr>
% 
% <tr>
% <td>Final Paper</td><td>10%</td>
% </tr>
% 
% <tr>
% <td>Final Exam</td><td>10%</td>
% </tr>
% 

\begin{center}
\begin{tabular}{ll}
Class Participation & 10\% \\
Instructor Meetings & 10\% \\
Short Writing Assignments & 50\% \\
Long Writing Assignments & 10\% \\
Presentation Assignments & 10\% \\
Final Examination & 10\%
\end{tabular}
\end{center}

\noindent
Each of the these grading categories has the following definition:

\begin{itemize}

	\item {\em Class Participation and Instructor Meetings}: All students are required to actively participate during
		all of the class sessions. Your participation will take forms such as answering questions about the required
		reading assignments, asking constructive questions of your group members, giving presentations, and leading a
		discussion session. Furthermore, all students are required to meet with the course instructor during office
		hours for a total of sixty minutes during the Fall 2013 semester.  These meetings must be scheduled through the
		course instructor's reservation system and documented on a meeting record that you submit on the day of the final
		examination. A student will receive an interim and final grade for this category.

	\item {\em First and Second Examinations}: The first and second interim examinations will cover all of the material
		in the associated module(s).  While the second examination is not cumulative, it will assume that a student has a
		basic understanding of the material that was the focus of the first examination.  The date for the first and
		second examinations will be announced at least one week in advance of the scheduled date.  Unless prior
		arrangements are made with the course instructor, all students will be expected to take these examinations on the
		scheduled date and complete the tests in the stated period of time.

	\item {\em Final Examination}: The final examination is a three-hour cumulative test.  By enrolling in the course,
		students agree that, unless there are extenuating circumstances, they will take the final examination at the
		time stated on the first page of the syllabus.

	\item {\em Laboratory and Homework Assignments}: These assignments invite students to explore the concepts, tools,
		and techniques that are associated with different phases of the software development life cycle.  All of the
		laboratory assignments require the use of the provided tools to design, implement, test, and maintain programs
		that solve important problems.  To ensure that students are ready to develop software in both other classes at
		Allegheny College and after graduation, the instructor will assign individuals to teams for each of the
		laboratory assignments.  Unless specified otherwise, each laboratory assignment will be due at the beginning of
		the next laboratory session.  Many of the laboratory assignments in this course will expect students to
		give both a presentation and a demonstration of the software that they specified, designed, implemented, tested,
		and documented.  
	
		%%% Homework assignments will normally ask students to prepare short written documents reflecting on
		% facets of the software development life cycles.

	\item {\em Final Project}: This project will present you with the description of a problem and require you to
		implement a full-featured solution using one or more programming languages and a wide variety of software
		development tools.  The final project in this class will require you to apply all of the knowledge and skills
		that you have accumulated during the course of the semester in order to solve a problem and, whenever possible,
		make your solution publicly available as a free and open-source tool.  The project will require you to draw upon
		both your problem solving skills and your knowledge of programming languages and software engineering tools. The
		final project will be completed in groups assigned by the course instructor.
		
\end{itemize}


\subsubsection*{Assignment Submission}

All assignments will have a stated due date. The printed version of the assignment is to be turned in at the beginning
of the class on that due date; the printed materials must be dated and signed with the Honor Code pledge of all the
students in the group.  The electronic version of the assignment must be available to the course instructor in a version
control repository when the printed version is submitted. Late assignments will be accepted for up to one week past the
assigned due date with a 10\% penalty. All late assignments must be submitted at the beginning of the session that is
scheduled one week after the due date. Unless special arrangements are made with the course instructor, no assignments
will be accepted after the late deadline. In addition to submitting the required deliverables for an assignment
completed in a group, students must turn in a one-page document that describes each group member's contribution to the
submitted deliverables.  

\subsubsection*{Attendance}

It is mandatory for all students to attend the class and laboratory sessions. If you will not be able to attend a
session, then please see the course instructor at least one week in advance to describe your situation.  Students who
miss more than five unexcused classes, laboratory sessions, or group project meetings will have their final grade in the
course reduced by one letter grade. Students who miss more than ten of the aforementioned events will automatically fail
the course.

% \subsection*{Laboratory Attendance Policy}
% 
% In order to acquired the proper skills in technical writing, critical reading, and the presentation of technical
% material, it is essential for students to have hands-on experience in a laboratory. Therefore, it is mandatory for all
% students to attend the laboratory sessions. If you will not be able to attend a laboratory, then please see the course
% instructors at least one week in advance in order to explain your situation. Students who miss more than two unexcused
% laboratories will have their final grade in the course reduced by one letter grade.  Students who miss more than four
% unexcused laboratories will automatically fail the course.
% 

\subsubsection*{Use of Laboratory Facilities}

Throughout the semester, we will experiment with many different tools that software engineers use during the phases of
the software development life cycle.  The course instructor and the department's systems administrator have invested a
considerable amount of time to ensure that our laboratories support the completion of both the laboratory assignments and the
final project.  To this end, students are required to complete all assignments and the final project while using the
department's laboratory facilities. The course instructor and the systems administrator will only be able to devote a
limited amount of time to the configuration of a student's personal computer.

\subsubsection*{Class Preparation}

% The study of the computer science discipline is very challenging.  Students in this class will be challenged to learn
% the principles and practice of software development.  During the coming semester even the most diligent student will
% experience times of frustration when they are attempting to understand a challenging concept or complete a difficult
% laboratory assignment.  In many situations some of the material that we examine will initially be confusing : do not
% despair!  Press on and persevere!
% 

In order to minimize confusion and maximize learning, students must invest time to prepare for class discussions and
lectures.  During the class periods, the course instructor will often pose demanding questions that could require group
consultation, the creation of a program or test suite, a vote on a thought-provoking issue, or a group presentation.
Only students who have prepared for class by reading the assigned material and reviewing the current assignments will be
able to effectively participate in these discussions.  More importantly, only prepared students will be able to acquire
the knowledge and skills that are needed to be successful in both this course and the field of software development.  In
order to help students remain organized and effectively prepare for classes, the course instructor will maintain a class
schedule with reading assignments and presentation slides.   During the class sessions students will also be required to
download, use, and modify programs, diagrams, and data sets that are made available through the course Web site.
Students who are not comfortable with compiling, editing, and running Java programs should see the course instructor.

\subsubsection*{Disability Services}

The Americans with Disabilities Act (ADA) is a federal anti-discrimination statute that provides comprehensive civil
rights protection for persons with disabilities.  Among other things, this legislation requires all students with
disabilities be guaranteed a learning environment that provides for reasonable accommodation of their disabilities.
Students with disabilities who believe they may need accommodations in this class are encouraged to contact Disability
Services at 332-2898.  Disability Services is part of the Learning Commons and is located in Pelletier Library.
Please do this as soon as possible to ensure that approved accommodations are implemented in a timely fashion.

\subsubsection*{Honor Code}

The Academic Honor Program that governs the entire academic program at Allegheny College is described in the Allegheny
Course Catalogue.  The Honor Program applies to all work that is submitted for academic credit or to meet non-credit
requirements for graduation at Allegheny College.  This includes all work assigned for this class (e.g., examinations,
laboratory assignments, and the final project).  All students who have enrolled in the College will work under the Honor
Program.  Each student who has matriculated at the College has acknowledged the following pledge:

\begin{quote}
I hereby recognize and pledge to fulfill my responsibilities, as defined in the Honor Code, and to maintain the
integrity of both myself and the College community as a whole.  
\end{quote}

\subsection*{Welcome to a Software Engineering Adventure}

In reference to software, Frederick Brooks, Jr.\ wrote in Chapter One of MMM, ``The magic of myth and legend has come true
in our time.'' Software is a pervasive aspect of our society that changes how we think and act.  High quality software
also has the potential to positively influence the lives of people. Moreover, the specification, design, implementation,
testing, maintenance, and documentation of software are exciting and rewarding activities!  At the start of this class,
I invite you to pursue this adventure in software engineering with enthusiasm and vigor.

\end{document}
